% This is a "bare-bones" thesis template file.  For examples of how to
% use a few more LaTeX features, look in the 'sample' folder.  Read
% the User Guide for documentation of the 'fsuthesis' class features.

\documentclass[12pt,expanded,copyright]{fsuthesis}
\input{mycommands}

% Additional packages may be loaded here.
\graphicspath{{figures/pMSSMpaper/distributions_1D_sel/}{figures/pMSSMpaper/distributions_2D_sel_sp/}{figures/pMSSMpaper/distributions_2D_sel/}{figures/pMSSMpaper/survprob_sel/}{figures/pMSSMpaper/distributions_Z/}}

% Do NOT use 'geometry' or 'setspace' packages! They will
% mess up the spacing provided by 'fsuthesis'.
%% These have been added at the request of the MIT Libraries, because
%% some PDF conversions mess up the ligatures.  -LB, 1/22/2014
\usepackage{cmap}
\usepackage[T1]{fontenc}
\pagestyle{plain}
\usepackage{rotating}
\usepackage[hidelinks]{hyperref}
\usepackage{placeins}
\usepackage{afterpage}


\title{Targeting the Minimal Supersymmetric Standard Model with the Compact Muon Solenoid Experiment}
\author{Samuel Louis Bein}
\college{College of Arts and Sciences}
\department{Department of Physics} % Delete if no department
\manuscripttype{Dissertation}              % [Thesis, Dissertation, Treatise]
\degree{Doctor of Philosophy}                 
\degreeyear{2016}
\defensedate{June 23, 2016}

%\subject{My Topic}
%\keywords{keyterm1; keyterm2; keyterm3; ...}

\committeeperson{Harrison B. Prosper}{Professor Directing Dissertation}
\committeeperson{Michael Ruse}{University Representative}
\committeeperson{Andrew Askew}{Committee Member}
\committeeperson{Takemichi Okui}{Committee Member}
\committeeperson{Jorge Piekarewicz}{Committee Member}

\clubpenalty=9999
\widowpenalty=9999

\begin{document}

\frontmatter
\maketitle
\makecommitteepage

%\begin{dedication}
%\end{dedication}

\begin{acknowledgments}
There are so many to thank for so much; this is my attempt. Thank you Harrison for one thousand good opportunities and a two thousand good ideas, and for letting me know that it doesn't matter where or how I train my multivariate discriminant, that even if Moses were to bring it down from the mountain top, I would be free to use it, provided I can reliably model its output in the data. Thank you Sabine for investing in me, for showing me what immunity to group think looks like, and for connecting me with so many who are now my colleagues. Thank you Sezen for persevering with me through the most challenging moments of the pMSSM paper (are they moments if they last for months and years?), and Lukas, Dipan, and Joe Bochenek for all the patience and generosity in the early years. Thank you Marc for making me quit using Mathematica and start using Root, and for having the world's biggest hard drive in your brain; I would not be finishing right now if it weren't for you. Thank you Keith and Bob for teaching me so much when you didn't have to, and for looking close enough to see value in my work. Thank you Hongxuan for having the most incredible sense of what the right research direction is; I realized that most of the things I did were things you encouraged early on. Thank you to Fermilab for hosting me so generously for two years; those years made all the difference; in that vein, thanks to Joe Pastika and Kevin Pedro for showing me so many ropes. Thank you Jory for reminding me to be a human being even though I'm a physicist. Thank you Jim and Jorge for getting me excited about nuclear physics, and for supporting me even though I did high energy. Thank you Take and Laura for caring so deeply about my education and always being willing to mentor. Thank you Andrew for putting an important fear of failure in me, and for reminding me to never use a jet veto, unless I'm totally desperate, and thank you Todd for magically having helpful, key information about every physics problem I ever discussed in your presence. Thank you Michael Ruse for agreeing to invest time in my work and managing to have an incredible amount of insight about subjects unrelated to your beat. Thank you Arka and Ajeeta for being my friends in addition to insightful work mates, and Daniel for being my most trusted physics consultant and friend; I hope our paths stay intertwined in the coming years. Thank you Rishi for expeditiously helping with the limit plots. Lastly, thanks to my family, Gloria, Rob, Bud, and Joe for the unthinkable amount of love and support throughout my PhD career, not to mention my entire life. 
\end{acknowledgments}

\tableofcontents
\listoftables
\listoffigures
%\listofmusex

%\begin{listofsymbols}
%\end{listofsymbols}

%\begin{listofabbrevs}
%\end{listofabbrevs}

\begin{abstract}
An interpretation of CMS searches for evidence of supersymmetry in the context of the minimal supersymmetric Standard Model (MSSM) is given. It is found that supersymmetric particles with color charge are excluded in the mass range below about 400 GeV, but neutral and weakly-charged sparticles remain non-excluded in all mass ranges. Discussion of the non-excluded regions of the model parameter space is given, including details on the strengths and weaknesses of existing searches, and recommendations for future analysis strategies. Advancements in the modeling of events arising from quantum chromodynamics and electroweak boson production, which are major backgrounds in searches for new physics at the LHC, are also presented. These methods have been implemented as components of CMS searches for supersymmetry in proton-proton collisions resulting in purely hadronic events (i.e., events with no identified leptons) at a center of momentum energy of 13 TeV. These searches, interpreted in the context of simplified models, exclude supersymmetric gluons (gluinos) up to masses of 1400 to 1600 GeV, depending on the model considered, and exclude scalar top quarks with masses up to about 800 GeV, assuming a massless lightest supersymmetric particle. A search for non-excluded supersymmetry models is also presented, which uses multivariate discriminants to isolate potential signal candidate events. The search achieves sensitivity to new physics models in background-dominated kinematic regions not typically considered by analyses, and rules out supersymmetry models that survived 7 and 8 TeV searches performed by CMS.
\end{abstract}

\mainmatter
\input{inputs/Introduction.tex}
\input{inputs/QFT.tex}
\input{inputs/StandardModel.tex}
\input{inputs/StandardModel/Problems.tex}
\input{inputs/ThisDocument.tex}
\input{inputs/Supersymmetry.tex}
\input{inputs/Experiment/LHC.tex}
\input{inputs/Experiment/CMS.tex}
%\input{inputs/Trigger.tex}
\input{inputs/pMSSM_CMS.tex}
\input{inputs/SusySearches.tex}
\input{inputs/Targeting.tex}
\input{inputs/Conclusion.tex}
%\bibliographystyle{plain}
\input{inputs/Appendices.tex}
\bibliography{myrefs}

%\input chapter1
%\input chapter2
%\input chapter3

%\appendix
%\input appendix1

% You have your choice of bibliography sections, either
% hand-crafted or BibTeX.


% Or use the BibTeX bibliography/references section below.  View the
% file 'myrefs.bib' to get a feel for what these entries may look
% like.  See the document in the 'sample' folder for more citation and
% BibTeX examples.



\begin{biosketch}
I attended the University of Colorado from 2007 to 2011, where I studied under the mentorship of theoretical nuclear physicist James R. Shepard. I conducted research on two- and three-nucleon interactions for my undergraduate honors thesis, and graduated with a bachelor's degree in physics and economics. From 2011 to 2016, I carried out research for my Ph.D. with Florida State University under the supervision of experimental particle physicist Harrison B. Prosper, and was based at the Fermi National Accelerator Laboratory for the final two years. This research included
\begin{itemize}
\item performing searches for supersymmetry in data collected by CMS;
\item performing interpretations of CMS searches based on the minimal supersymmetric standard model;
\item developing techniques for the modeling of standard model processes that are backgrounds to new physics searches;
\item developing hardware and software for test beam experiments to study and characterize future components of the CMS detector;
\item contributing to the creation of a database of public implementations of CMS and ATLAS searches for use by physicists outside the collaborations.
\end{itemize}
I defended my dissertation in June, 2016. In the fall of 2016, I will begin a postdoctoral fellowship with the University of Hamburg, where I will help to carry out searches for evidence of new physics with the CMS experiment and develop hardware for the CMS silicon tracker.
\end{biosketch}

\end{document}
