\section*{Acknowledgments}
There are too many to thank for too much, but i will try. Thank you Harrison for one thousand good opportunities and a two thousand good ideas, and for letting me know that it doesn't matter where or how I train my multivariate discriminant, that even if Moses were to bring it down from the mountain top, I would be free to use it, provided I can reliably model its output in the data. Thank you Sabine for investing in me, for showing me what immunity to group think looks like, and for connecting me with so many of who are now my colleagues. Thank you Sezen for persevering with me through the most challenging moments of the pMSSM paper (are they moments if they last for months and years?), and Lukas and Joe Bocheneck for all the patience and generosity in the early years. Thank you Marc for making me quit using Mathematica and start using Root, and for having the world's biggest hard drive in your brain; I would not be finishing right now if it weren't for you. Thank you Keith and Bob for teaching me so much when you didn't have to, and for looking close enough to see value in my work. Thank you Hongxuan for having the most incredible sense of what the right research direction is; I realized that most of the things I did were things you encouraged early on. Thank you to Fermilab for hosting me so generously for two years; those years made all the difference; Joe Pastika, Nadja Strobe, and Kevin Pedro for good measure. Thank you Jory for reminding me to be a human being even though I'm a physicist. Thank you Jim and Jorge for getting me excited about nuclear physics, and for accepting me even though I did high energy. Thank you Take and Laura for caring so deeply about my education and always being wiling to mentor. Thank you Andrew for putting the fear of failure in me, and for reminding me to never use a jet veto, unless I'm totally desperate, and thank you Todd for magically having helpful, key information about every physics problem I ever discussed in your presence. Thank you Michael Reuse for agreeing to invest time in me and managing to have an astonishing amount of insight about subjects unrelated to your beat. Thank you Arka and Ajeeta for being my friends in addition to insightful work mates, and Daniel for being my most trusted physics consultant and friend; I hope our paths stay intertwined in the coming years. Lastly, thanks to my family, Gloria, Rob, Bud, and Joe for the unthinkable amount of love and support throughout my PhD career, not to mention my entire life. 