\chapter{CMS Searches for Supersymmetry at $\sqrt{s}=13$ TeV}
\label{chap:susysearches}
One of the findings of Chapter~\ref{chap:run1pmssm}, and seen in Fig.~\ref{fig:Z}, is that searches for SUSY events with purely hadronic final states have a particularly significant impact on our knowledge of the MSSM. Furthermore, it was found that SUSY models characterized by large fiducial cross sections corresponding to low thresholds on the $\met$, $\Ht$, and $\njets$ survived 7 and 8 TeV CMS searches. 

After making these findings, I contributed to CMS hadronic analyses \cite{Khachatryan:2016kdk} and \cite{CMS:2016nhb}, where I developed methods that increase the sensitivity of the searches to SUSY models that predict large numbers of events produced in the low-$\met$ and low-$\Ht$ regions. The primary backgrounds in these regions are multi-jet events arising from QCD interactions, and events arising from the electroweak production of a Z boson that decays into neutrinos, Z$\rightarrow\nu\bar{\nu}$. I developed a data-driven QCD event simulator, based on the rebalance and smear method, that allows the prediction of QCD background counts to be made with uncertainties that are lower than those of alternative methods by up to an order of magnitude; I developed and performed a data-driven $\zinv$ background estimation method that uses events in which a Z boson is produced and decays into two electrons or two muons as a proxy for $\zinv$ background events. I also built upon a technique that maximizes the usefulness of triggers in kinematic regions in which the trigger is not fully turned on. 

The above techniques are discussed generally in the following sections, that is, they are discussed as stand-alone methods, independent of a particular analysis, with only occasional reference made to the analyses in which the methods were applied. The aim of this approach is to accentuate the universality of the techniques. In particular, as the above methods were implemented, special effort was paid to ensure that the methods remain valid in kinematics regions with lower $\met$ and $\Ht$ than the baseline regions of the hadronic analyses. Then, Section \ref{sec:2015results} discusses how these methods have been applied specifically in the context of two high-$\met$ hadronic searches: the multi-jet + $\mht$ search \cite{Khachatryan:2016kdk}, and the search for SUSY with top squarks \cite{CMS:2016nhb}. Section \ref{sec:2015results} gives a brief introduction to the analyses \cite{Khachatryan:2016kdk} and \cite{CMS:2016nhb}, a detailing of the baseline selection, a discussion of the background estimates and uncertainties obtained using the above methods, and the final results of the searches, namely, limits on sparticle masses set in the context of simplified models.  Then, in the chapter that follows, I explore the use of multivariate techniques in background-dominated kinematic regions like the low-$\met$ region and the low-$\Ht$ region, as a way to probe nonexcluded pMSSM points. 


\section{Trigger methods}
\label{sec:anatrig}
\input{inputs/SusySearches/AnalysisTrigger.tex}

\section{QCD background estimation}
\label{sec:qcd}
\input{inputs/SusySearches/RplusS.tex}

\section{Z$\rightarrow\nu\bar{\nu}$ background estimation}
\label{sec:zinv}
\input{inputs/SusySearches/ZInv.tex}



\section{Results of 2015 SUSY searches}
\label{sec:2015results}
The QCD background estimation, $\zinv$ background estimation, and trigger techniques just described were carried out in the context of two CMS SUSY searches. This section briefly describes these analyses, their baseline selection and search region definitions, the primary backgrounds, and an interpretation of their findings in terms of various simplified models. 

This section also gives the predictions and and systematic uncertainties of the background estimation methods in the search bins of the two hadronic analyses. I note that the following results are the product of the work of dozens of analysis team members, and the work I have described above constitutes a few ingredients of a collaborative effort. The searches are based on a sample of proton-proton collision data collected at $\sqrt{s}=13~\TeV~$ with the CMS detector at the CERN LHC in 2015, corresponding to an integrated luminosity of 2.3 fb$^{-1}$.

\subsection{Multi-jet $+$ $\mht$ SUSY search: targeting gluino production at $\sqrt{s}=13$ TeV}
\label{sec:ra2b2015}
\input{inputs/SusySearches/Ra2b2015.tex}
\FloatBarrier

\subsection{Search for SUSY in events with top-tagged jets at $\sqrt{s}=13$ TeV}
\label{sec:hadstop2015}
\input{inputs/SusySearches/HadStop2015.tex}
\FloatBarrier

\chapter{Targeting the Non-Excluded pMSSM with Multivariate Discriminants}
\label{chap:money}
\FloatBarrier
